Interval-Valued Quantum Probabilities: Contextuality and the Born Rule

### 2017-07-06 prop_letter.tex
minor changes up in first three sections

\begin{abstract}~
\begin{description}
\item [{Background}] In a world of bounded resource, any quantum measurement
can be only performed in finite precision.
\item [{Method}] We model the idea of the finite precision measurement
as finite number of intervals, and replace quantum real-valued probability
measures by interval-valued ones.
\item [{Results}] Quantum interval-valued probability measures provide
a unified framework to interpret Gleason's theorem and the Kochen-Specker
theorem as the limiting cases. For the cases between them, we found
some legitimate quantum interval-valued probability measures which
cannot be explained by the Born rule. While restricting on only commuting
projectors, the interval-valued probability measures become classical,
and these non-Born interval-valued probability measures disappear.
\item [{Conclusions}] Our research provides a new insight of finite precision
measurement and non-commutativity when formulating quantum theory.
Also, the Born rule may not be as nature as we used to believe in
the world of finite resource.
\end{description}
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Introduction}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Fuzzy Measurements}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Intervals of Uncertainty}

We will start by reviewing IVPMs in the classical setting
and then propose our quantum generalization. In the classical setting,
there are several proposals for ``imprecise
probabilities\nb\citep{Dempster1967,Artstein1972,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,Galvan2008,HuberRonchetti2009,Grabisch2016}.''
Although these proposals differ in some details, they all share the
fact that the probability $\mu(E)$ of an event $E$ is generalized
from a single real number to an interval of certainty $[\ell,r]$
where\nb$\ell$ intuitively corresponds to the strength of evidence
for the event and $r$ corresponds to the strength of evidence against
the event. The collection of intervals used in the definition of a
probability measure must satisfy certain properties which we explain
next.

First for each interval $[\ell,r]$ we have the natural constraint
$0 \leq \ell \leq r \leq 1$ that guarantees that every element of the
interval can be interpreted as a conventional probability. We also
include $\imposs=[0,0]$ and $\necess=[1,1]$ as limiting intervals to
refer to the probability of impossible events (e.g., the null event)
and certain events (e.g., the event covering the entire sample space).
For each interval $[\ell,r]$, we also need the interval
$[1-r,1-\ell]$ so that if one interval refers to the probability of an
event, the other refers to the probability of the complement
event. For example, if we discover as a result of an experiment that
$\mu(E) = [0.2,0.3]$ for some event\nb$E$, we may conclude that
$\mu(\overline{E}) = [0.7,0.8]$ for the complement event
$\overline{E}$. In addition to these simple conditions, there are some
subtle conditions on how intervals are combined, which we discuss
next.

@@

When combining non-disjoint events, there is a further subtlety whose
resolution will give the most general and final condition as
follows. For general, non-necessarily disjoint events $E_1$ and $E_2$,
we have:
\begin{equation}
\mu(E_1\cup E_2) + \mu(E_1\cap E_2) \subseteq \mu(E_1) + \mu(E_2)
\label{eq:classicalconvex}
\end{equation}
which is a generalization of the classical inclusion-exclusion
principle that uses $\subseteq$ instead of $=$ for the same reason as
before. The new condition, known as
\emph{convexity}\nb\cite{Shapley1971,GilboaSchmeidler1994,Marinacci1999,Grabisch2016},
reduces to the previously
motivated condition when the events are disjoint, i.e., when
$\mu(E_1\cap E_2) = 0$.

@@

\begin{definition}[QIVPM]
  Given a collection of intervals $\mathscr{I}$ including
  $\imposs=[0,0]$ and $\necess=[1,1]$ and with addition and scalar
  multiplication defined as follows:
  \begin{subequations}\label{eq:interval-operations}
  \begin{eqnarray}
   &  & [\ell_{1},r_{1}]+[\ell_{2},r_{2}]=[\ell_{1}+\ell_{2},r_{1}+r_{2}]\textrm{ and}\\
   &  & x[\ell,r]=\begin{cases}
  [x\ell,xr] & \textrm{for }x\ge0\,;\\{}
  [xr,x\ell] & \textrm{for }x\le0\,,
  \end{cases}
  \end{eqnarray}
  \end{subequations}
  a QIVPM $\bar{\mu}$ is an assignment of an interval to each event
  (projection operator) subject to the following constraints:
  $\bar{\mu}(\mathbb{0})=\left[0,0\right]$,
  $\bar{\mu}(\mathbb{1})=\left[1,1\right]$,
  $\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$,
  and for each pair of \emph{commuting} projections $P_0$ and $P_1$,
  we have:
\begin{equation}
\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)
\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\end{definition}
The first three constraints are the direct counterpart of the
corresponding ones for conventional probability measures. With the
understanding that the union of classical sets $E_1\cup E_2$ is replaced
by $P_0+P_1-P_0P_1$ in the case of projection operators\nb\cite{Griffiths2003}, the last
condition, Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion}, is
a direct counterpart of Eq.~\ref{eq:classicalconvex}.

Contrary to the case with conventional quantum probability spaces,
there is generally no unique state consistent with a QIVPM. Given
observations done with finite resources, the probabilities become
intervals, and we say a state\nb$\rho$ is consistent with $\bar{\mu}$ on
a projector\nb$P$ if
$\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$, and
denoted by
$\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$,
where $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\Tr\left(\rho P\right)$
is the probability that the event\nb$P$ happens determined by the
Born rule\nb\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means $\rho$ is
consistent with $\bar{\mu}$ on every projector in $S$.

@@

For example, assuming the three intervals \imposs, \necess, and
$\unknown=\left[0,1\right]$, then:
\begin{equation}
\bar{\mu}_{1}\left(P\right)=\begin{cases}
\necess\,, & \text{if }P=\mathbb{1}\text{ ;}\\
\imposs\,, & \text{if }P=\mathbb{0}\text{ ;}\\
\unknown\,, & \text{otherwise,}
\end{cases}\label{eq:no-information-IVPM}
\end{equation}
is a quantum IVPM. This measure represents the beliefs of an
experimenter with no prior knowledge about the particular quantum
system in question; any quantum state would be consistent with
$\bar{\mu}_{1}$ on any projectors. We have that
$\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ on
$\events_{0}$, $\bar{\mu}_{1}|_{\events_{0}}$, gives a classical
IVPM\nb$\bar{\mu}_{2}$:
\begin{equation}
\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
\end{aligned}
\,.
\end{equation}
If we identify the density matrices\nb$\proj{0}$ and $\proj{1}$ as
the head and the tail of a coin, respectively, then $\bar{\mu}_{2}$
represents that an experimenter knows nothing about a coin before
she tosses it. Moreover, for each $p\in\left[0,1\right]$, the mixed
state\nb$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical
coin with probability\nb$p$ to get head, and $p\proj{0}+\left(1-p\right)\proj{1}$
is consistent with $\bar{\mu}_{2}$ on $\events_{0}$ because any
classical coin should be consistent with the situation where an experimenter
has no prior knowledge.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Kochen-Specker}

Our first result regarding QIVPM is that a QIVPM cannot be
cryptodeterministic in the sense of Peres\nb\cite{PeresRon1988,peres1995quantum}. We
will adapt the proof of the Kochen-Specker
theorem\nb\cite{kochenspecker1967,
  peres1995quantum,Redhead1987-REDINA,Griffiths2003} to show that it
is, in general, impossible to just have the two intervals \imposs\ and
\necess: every QIVPM must be parameterized by a collection of
intervals that includes at least one additional ``fuzzy'' interval and
some events must be associated with such uncertain intervals. The
significance of this observation is that the uncertainty in the
intervals is, in contrast to the classical case, \emph{a fundamental
  part of quantum theory}. There are in fact two sources of
uncertainty: one due to the finite measurement resources and one due
to complementarity which requires every quantum framework to be truly
probabilistic.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Gleason}

@@

Gleason's theorem asserts any quantum real-valued probability measure
is consistent with a unique mixed state, and Shapley proved a quantum
IVPM must approximate some states for each classical sub-event
space. However, it may not approximate the same state in every
sub-event space. As the result, there may be no state consistent with
a quantum IVPM on all projectors\nb$\events$.

\begin{example}\label{ex:three-dimensional-three-value}
  Given a three dimensional Hilbert space with an orthonormal basis
  $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.  Let
  $\mathscr{I}_{1}=\left\{ \necess,\imposs,\unknown\right\} $,
  $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
  $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$, and
\begin{subequations}
\begin{eqnarray}
 &  & \begin{aligned}\imposs & =\bar{\mu}_{3}(\mathbb{0})=\bar{\mu}_{3}(\proj{0})\\
 & =\bar{\mu}_{3}(\proj{\ps})=\bar{\mu}_{3}(\proj{\ps'})\,,
\end{aligned}
\\
 &  & \begin{aligned}\necess & =\bar{\mu}_{3}(\mathbb{1})=\bar{\mu}_{3}(\mathbb{1}-\proj{0})\\
 & =\bar{\mu}_{3}(\mathbb{1}-\proj{\ps})=\bar{\mu}_{3}(\mathbb{1}-\proj{\ps'})\,,
\end{aligned}
\\
 &  & \unknown=\bar{\mu}_{3}(P)\qquad\textrm{otherwise.}
\end{eqnarray}
\end{subequations}
It is straightforward to verify that $\bar{\mu}_{3}$ is a
quantum IVPM.

@@

Although Gleason's theorem doesn't hold for every quantum IVPM, if
a quantum IVPM\nb$\bar{\mu}$ is induced by a totally mixed state\nb$\rho$
nicely, then whether another density matrix\nb$\rho'\in\coreBorn\left(\bar{\mu},\events'\right)$
can be estimated by $\left\Vert \rho-\rho'\right\Vert $, where a
state\nb$\rho$ is called totally mixed if $0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$
for any $P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $,
and the the norm of a matrix\nb$A$ is defined by $\left\Vert A\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{A}{\psi}\right|$\nb\citep{544199}.
For example, consider the intervals
\begin{eqnarray}
\widehat{\mathscr{I}}_{n} & = & \set{\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\nonumber \\
 &  & \cup\left\{ \left[0,0\right],\left[1,1\right]\right\} 
\end{eqnarray}
which are overlapping intervals with length\nb$1/n$ except the intervals
near the ends. We can define an interval-valued function\nb$\widehat{\iota}_{n}:\left[0,1\right]\rightarrow\widehat{\mathscr{I}}_{n}$
by the following:
\begin{itemize}
\item when $x=0$ or $x=1$, $\widehat{\iota}_{n}\left(x\right)=\left[x,x\right]$;
\item when $0<x<1$, $\widehat{\iota}_{n}\left(x\right)=\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]$,
where $k$ is defined by one of the following:
\begin{itemize}
\item $2\mid k$ and $k-0.5\le2nx\le k+0.5$;
\item $2\nmid k$ and $k-0.5<2nx<k+0.5$.
\end{itemize}
\end{itemize}
Then, for any totally mixed state\nb$\rho$ on a $d$-dimensional
Hilbert space, $\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$
is a QIVPM, and we have
\begin{itemize}
\item If $\left\Vert \rho-\rho'\right\Vert \le1/\left(4dn\right)$, $\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.
\item If $\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
then $\left\Vert \rho-\rho'\right\Vert \le1/n$.
\end{itemize}
In summary, the states consistent with $\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$
will be closer and closer to $\rho$ as $n$ goes to infinity. In
a limit case when the intervals are infinitely precise, i.e., $\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
any quantum IVPM can be recast as an real-valued one and has a unique
state consistent with it on every projector when $d\ge3$.

In general, this kind of inconsistency can be reduced if we increase
the measurement resource, that is, using finer intervals. We conjecture
by using finer and finer intervals, it would be more and more likely
that there is a state consistent with a quantum IVPM on all projectors\nb$\events$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Conclusion}

@@

To adapt the axioms of such IVPMs to the quantum case, we proceed as
follows. First we fix a collection of intervals $\mathscr{I}$ that
represents an abstraction of the available experimental resources. At
one extreme, infinitely precise resources would correspond to the
collection of intervals $\{[x,x] \mid x \in [0,1]\}$. This case should
coincide with the idealized situation above. At another extreme, an
experiment with ``minimal'' resources would correspond to the
following three intervals $\imposs=\left[0,0\right]$,
$\necess=\left[1,1\right]$, and $\unknown=[0,1]$. As before, the first
two intervals are associated with the empty projection and the
identity projection but every other projection would be associated
with $\unknown$; its probability can be anything in the range
$[0,1]$. A third special situation would be to consider IVPMs with
only the two intervals $\imposs=\left[0,0\right]$ and
$\necess=\left[1,1\right]$. This is what Peres calls the
\emph{cryptodeterministic} case in which there is no ambiguity about
the status of any event; we know for certain if it will occur or not.

\begin{definition}
$\bar{\mu}$ is called convex. if for all
commuting $P_{0},P_{1}\in\events$, we have
$\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.
\end{definition}

Consider again
Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion}. We will
generalize it as follows for all commuting $P_{0},P_{1}\in\events$, we
have
$\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$. Note
that if $P_0$ and $P_1$ are \emph{orthogonal}, i.e., if $P_0P_1=0$ the
new equation reduces to
Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion}.

\begin{verbatim}
Inclusion exclusion principle 
 pr(e1 union e2) + pr (e1 intersect e2) = 
  pr(e1) + pr(e2)

in classical Real number prob. LHS = X; RHS = X

---

in classical IVPM; we only get LHS <= X; RHS <= X
but we have no connection between LHS and RHS

convexity imposes that LHS >= RHS

---

our condition in the quantum case is the same; 
our left(LHS) is >= left(RHS); the right is dual, 
which makes LHS interval subset RHS interval.

--

replace set union by projection sum = p0 + p1 - p0p1
replace = by subseteq

and we get convexity definition

--

Now we need a simple classical example that shows 
why we need convexity or at least what it means

must be dimension 4 because everything of dim 3 
is convex in classical case

>>>>

\begin{abstract}~
\amr{rewrite from scratch}
\begin{description}
\item [{Background}] In a world of bounded resource, any quantum measurement
can be only performed in finite precision.
\item [{Method}] We model the idea of the finite precision measurement
as finite number of intervals, and replace quantum real-valued probability
measures by interval-valued ones.
\item [{Results}] Quantum interval-valued probability measures provide
a unified framework to interpret Gleason's theorem and the Kochen-Specker
theorem as the limiting cases. For the cases between them, we found
some legitimate quantum interval-valued probability measures which
cannot be explained by the Born rule. While restricting on only commuting
projectors, the interval-valued probability measures become classical,
and these non-Born interval-valued probability measures disappear.
\item [{Conclusions}] Our research provides a new insight of finite precision
measurement and non-commutativity when formulating quantum theory.
Also, the Born rule may not be as nature as we used to believe in
the world of finite resource.
\end{description}
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fuzzy Measurements}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Intervals of Uncertainty}

We will start by reviewing IVPMs in the classical setting and then
propose our quantum generalization. In the classical setting, there
are several proposals for ``imprecise
probabilities''~\citep{Dempster1967,Artstein1972,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,Galvan2008,HuberRonchetti2009,Grabisch2016}.
Although these proposals differ in some details, they all share the
fact that the probability $\mu(E)$ of an event~$E$ is generalized from
a single real number to an interval of certainty $[\ell,r]$
where\nb$\ell$ intuitively corresponds to the strength of evidence for
the event and~$r$ corresponds to the strength of evidence against the
event. The collection of intervals used in the definition of a
probability measure must satisfy certain properties which we explain
next.

First for each interval $[\ell,r]$ we have the natural constraint
$0 \leq \ell \leq r \leq 1$ that guarantees that every element of the
interval can be interpreted as a conventional probability. We also
include $\imposs=[0,0]$ and $\necess=[1,1]$ as limiting intervals to
refer to the probability of impossible events (e.g., the null event)
and certain events (e.g., the event covering the entire sample space).
For each interval $[\ell,r]$, we also need the interval
$[1-r,1-\ell]$ so that if one interval refers to the probability of an
event, the other refers to the probability of the complement
event. For example, if we discover as a result of an experiment that
$\mu(E) = [0.2,0.3]$ for some event~$E$, we may conclude that
$\mu(\overline{E}) = [0.7,0.8]$ for the complement event
$\overline{E}$. In addition to these simple conditions, there are some
subtle conditions on how intervals are combined, which we discuss
next.

@@

When combining non-disjoint events, there is a further subtlety whose
resolution will give the most general and final condition. For
general, non-necessarily disjoint events $E_1$ and $E_2$, we have:
\begin{equation}
\mu(E_1\cup E_2) + \mu(E_1\cap E_2) \subseteq \mu(E_1) + \mu(E_2)
\label{eq:classicalconvex}
\end{equation}
which is a generalization of the classical inclusion-exclusion
principle that uses $\subseteq$ instead of $=$ for the same reason as
before. The new condition, known as
\emph{convexity}\nb\cite{Shapley1971,GilboaSchmeidler1994,Marinacci1999,Grabisch2016},
reduces to the previously
motivated condition when the events are disjoint, i.e., when
$\mu(E_1\cap E_2) = 0$.

@@

\begin{definition}[QIVPM]
  Given a collection of intervals $\mathscr{I}$ including
  $\imposs=[0,0]$ and $\necess=[1,1]$ and with addition and scalar
  multiplication defined as follows:
  \begin{subequations}\label{eq:interval-operations}
  \begin{eqnarray}
   &  & [\ell_{1},r_{1}]+[\ell_{2},r_{2}]=[\ell_{1}+\ell_{2},r_{1}+r_{2}]\textrm{ and}\\
   &  & x[\ell,r]=\begin{cases}
  [x\ell,xr] & \textrm{for }x\ge0\,;\\{}
  [xr,x\ell] & \textrm{for }x\le0\,,
  \end{cases}
  \end{eqnarray}
  \end{subequations}
  a QIVPM $\bar{\mu}$ is an assignment of an interval to each event
  (projection operator) subject to the following constraints:
  $\bar{\mu}(\mathbb{0})=\left[0,0\right]$,
  $\bar{\mu}(\mathbb{1})=\left[1,1\right]$,
  $\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$,
  and for each pair of \emph{commuting} projections $P_0$ and $P_1$,
  we have:
\begin{equation}
\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)
\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\end{definition}
The first three constraints are the direct counterpart of the
corresponding ones for conventional probability measures. With the
understanding that the union of classical sets $E_1\cup E_2$ is replaced
by $P_0+P_1-P_0P_1$ in the case of projection operators~\cite{Griffiths2003}, the last
condition, Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion}, is
a direct counterpart of Eq.~\ref{eq:classicalconvex}.

Contrary to the case with conventional quantum probability spaces,
there is generally no unique state consistent with a QIVPM. Given
observations done with finite resources, the probabilities become
intervals, and we say a state\nb$\rho$ is consistent with $\bar{\mu}$ on
a projector\nb$P$ if
$\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$, and
denoted by
$\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$,
where $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\Tr\left(\rho P\right)$
is the probability that the event\nb$P$ happens determined by the
Born rule\nb\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means~$\rho$ is
consistent with $\bar{\mu}$ on every projector in $S$.

@@

For example, assuming the three intervals \imposs, \necess, and
$\unknown=\left[0,1\right]$, then:
\begin{equation}
\bar{\mu}_{1}\left(P\right)=\begin{cases}
\necess\,, & \text{if }P=\mathbb{1}\text{ ;}\\
\imposs\,, & \text{if }P=\mathbb{0}\text{ ;}\\
\unknown\,, & \text{otherwise,}
\end{cases}\label{eq:no-information-IVPM}
\end{equation}
is a QIVPM. This measure represents the beliefs of an experimenter
with no prior knowledge about the particular quantum system in
question; any quantum state would be consistent with $\bar{\mu}_{1}$
on any projectors. We have that
$\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ on
$\events_{0}$, $\bar{\mu}_{1}|_{\events_{0}}$, gives a classical
IVPM~$\bar{\mu}_{2}$:
\begin{equation}
\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
\end{aligned}
\,.
\end{equation}
If we identify the density matrices\nb$\proj{0}$ and $\proj{1}$ as
the head and the tail of a coin, respectively, then $\bar{\mu}_{2}$
represents that an experimenter knows nothing about a coin before
she tosses it. Moreover, for each $p\in\left[0,1\right]$, the mixed
state\nb$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical
coin with probability\nb$p$ to get head, and $p\proj{0}+\left(1-p\right)\proj{1}$
is consistent with $\bar{\mu}_{2}$ on $\events_{0}$ because any
classical coin should be consistent with the situation where an experimenter
has no prior knowledge.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Kochen-Specker}

Our first result is that a QIVPM cannot be cryptodeterministic in the
sense of Peres\nb\cite{PeresRon1988,peres1995quantum}. We will adapt
the proof of the Kochen-Specker theorem~\cite{kochenspecker1967,
  peres1995quantum,Redhead1987-REDINA,Griffiths2003} to show that it
is, in general, impossible to just have the two intervals \imposs\ and
\necess: every QIVPM must be parameterized by a collection of
intervals that includes at least one additional ``fuzzy'' interval and
some events must be associated with such uncertain intervals. The
significance of this observation is that the uncertainty in the
intervals is, in contrast to the classical case, \emph{a fundamental
  part of quantum theory}. There are in fact two sources of
uncertainty: one due to the finite measurement resources and one due
to complementarity which requires every quantum framework to be truly
probabilistic.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Gleason}

@@

Gleason's theorem asserts any quantum real-valued probability measure
is consistent with a unique mixed state, and Shapley proved a quantum
IVPM must approximate some states for each classical sub-event
space. However, it may not approximate the same state in every
sub-event space. As the result, there may be no state consistent with
a QIVPM on all projectors\nb$\events$.

\begin{example}\label{ex:three-dimensional-three-value}
  Given a three dimensional Hilbert space with an orthonormal basis
  $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.  Let
  $\mathscr{I}_{1}=\left\{ \necess,\imposs,\unknown\right\} $,
  $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
  $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$, and
\begin{subequations}
\begin{eqnarray}
 &  & \begin{aligned}\imposs & =\bar{\mu}_{3}(\mathbb{0})=\bar{\mu}_{3}(\proj{0})\\
 & =\bar{\mu}_{3}(\proj{\ps})=\bar{\mu}_{3}(\proj{\ps'})\,,
\end{aligned}
\\
 &  & \begin{aligned}\necess & =\bar{\mu}_{3}(\mathbb{1})=\bar{\mu}_{3}(\mathbb{1}-\proj{0})\\
 & =\bar{\mu}_{3}(\mathbb{1}-\proj{\ps})=\bar{\mu}_{3}(\mathbb{1}-\proj{\ps'})\,,
\end{aligned}
\\
 &  & \unknown=\bar{\mu}_{3}(P)\qquad\textrm{otherwise.}
\end{eqnarray}
\end{subequations}
It is straightforward to verify that $\bar{\mu}_{3}$ is a QIVPM.

@@

Although Gleason's theorem doesn't hold for every QIVPM, if a quantum
IVPM\nb$\bar{\mu}$ is induced by a totally mixed state\nb$\rho$
nicely, then whether another density
matrix\nb$\rho'\in\coreBorn\left(\bar{\mu},\events'\right)$ can be
estimated by $\left\Vert \rho-\rho'\right\Vert $, where a
state\nb$\rho$ is called totally mixed if
$0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$ for any
$P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $, and the
the norm of a matrix\nb$A$ is defined by
$\left\Vert A\right\Vert
=\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{A}{\psi}\right|$\nb\citep{544199}.
For example, consider the intervals
\begin{eqnarray}
\widehat{\mathscr{I}}_{n} & = & \set{\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\nonumber \\
 &  & \cup\left\{ \left[0,0\right],\left[1,1\right]\right\} 
\end{eqnarray}
which are overlapping intervals with length\nb$1/n$ except the intervals
near the ends. We can define an interval-valued function\nb$\widehat{\iota}_{n}:\left[0,1\right]\rightarrow\widehat{\mathscr{I}}_{n}$
by the following:
\begin{itemize}
\item when $x=0$ or $x=1$, $\widehat{\iota}_{n}\left(x\right)=\left[x,x\right]$;
\item when $0<x<1$, $\widehat{\iota}_{n}\left(x\right)=\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]$,
where $k$ is defined by one of the following:
\begin{itemize}
\item $2\mid k$ and $k-0.5\le2nx\le k+0.5$;
\item $2\nmid k$ and $k-0.5<2nx<k+0.5$.
\end{itemize}
\end{itemize}
Then, for any totally mixed state\nb$\rho$ on a $d$-dimensional
Hilbert space, $\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$
is a QIVPM, and we have
\begin{itemize}
\item If $\left\Vert \rho-\rho'\right\Vert \le1/\left(4dn\right)$, $\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.
\item If $\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
then $\left\Vert \rho-\rho'\right\Vert \le1/n$.
\end{itemize}
In summary, the states consistent with
$\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$ will be closer and
closer to $\rho$ as $n$ goes to infinity. In a limit case when the
intervals are infinitely precise, i.e.,
$\set{\left[x,x\right]}{x\in\left[0,1\right]}$, any QIVPM can be
recast as an real-valued one and has a unique state consistent with it
on every projector when $d\ge3$.

In general, this kind of inconsistency can be reduced if we increase
the measurement resource, that is, using finer intervals. We conjecture
by using finer and finer intervals, it would be more and more likely
that there is a state consistent with a QIVPM on all projectors\nb$\events$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}

@@

% To adapt the axioms of such IVPMs to the quantum case, we proceed as
% follows. First we fix a collection of intervals $\mathscr{I}$ that
% represents an abstraction of the available experimental resources. At
% one extreme, infinitely precise resources would correspond to the
% collection of intervals $\{[x,x] \mid x \in [0,1]\}$. This case should
% coincide with the idealized situation above. At another extreme, an
% experiment with ``minimal'' resources would correspond to the
% following three intervals $\imposs=\left[0,0\right]$,
% $\necess=\left[1,1\right]$, and $\unknown=[0,1]$. As before, the first
% two intervals are associated with the empty projection and the
% identity projection but every other projection would be associated
% with $\unknown$; its probability can be anything in the range
% $[0,1]$. A third special situation would be to consider IVPMs with
% only the two intervals $\imposs=\left[0,0\right]$ and
% $\necess=\left[1,1\right]$. This is what Peres calls the
% \emph{cryptodeterministic} case in which there is no ambiguity about
% the status of any event; we know for certain if it will occur or not.

% \begin{definition}
% $\bar{\mu}$ is called convex. if for all
% commuting $P_{0},P_{1}\in\events$, we have
% $\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.
% \end{definition}

% Consider again
% Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion}. We will
% generalize it as follows for all commuting $P_{0},P_{1}\in\events$, we
% have
% $\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$. Note
% that if $P_0$ and $P_1$ are \emph{orthogonal}, i.e., if $P_0P_1=0$ the
% new equation reduces to
% Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion}.

% \begin{verbatim}
% Inclusion exclusion principle 
%  pr(e1 union e2) + pr (e1 intersect e2) = 
%   pr(e1) + pr(e2)

% in classical Real number prob. LHS = X; RHS = X

% ---

% in classical IVPM; we only get LHS <= X; RHS <= X
% but we have no connection between LHS and RHS

% convexity imposes that LHS >= RHS

% ---

% our condition in the quantum case is the same; 
% our left(LHS) is >= left(RHS); the right is dual, 
% which makes LHS interval subset RHS interval.

% --

% replace set union by projection sum = p0 + p1 - p0p1
% replace = by subseteq

% and we get convexity definition

% --

% Now we need a simple classical example that shows 
% why we need convexity or at least what it means
